%%% Zhejiang University of Technology 
%%% !Mode\dots "TeX:UTF-8"
%%% author : liuzheng712@gmail.com(刘正)

\LaTeX\ (formatted as LATEX, pronounced /ˈlɑːtɛx/, /ˈlɑːtɛk/, /ˈleɪtɛx/, or /ˈleɪtɛk/), is a document markup language and document preparation system for the \TeX\ typesetting program. The term \LaTeX\ refers only to the language in which documents are written, not to the editor application used to write those documents. In order to create a document in \LaTeX\ , a .tex file must be created using some form of text editor. While most text editors can be used to create a \LaTeX\ document, a number of editors have been created specifically for working with \LaTeX\ .

\LaTeX\ is widely used in academia.\cite{WrTex,Alexia} It is also used as the primary method of displaying formulas on Wikipedia. As a primary or intermediate format, e.g., translating DocBook and other XML-based formats to PDF, \LaTeX\ is used because of the high quality of typesetting achievable by \TeX\ . The typesetting system offers programmable desktop publishing features and extensive facilities for automating most aspects of typesetting and desktop publishing, including numbering and cross-referencing, tables and figures, page layout and bibliographies.

\LaTeX\ is intended to provide a high-level language that accesses the power of \TeX\ . \LaTeX\ essentially comprises a collection of \TeX\ macros and a program to process \LaTeX\ documents. Because the \TeX\ formatting commands are very low-level, it is usually much simpler for end-users to use \LaTeX\ .

\LaTeX\ was originally written in the early 1980s by Leslie Lamport at SRI International.\cite{Leslie} The current version is \LaTeXe\ (styled as \LaTeXe\ ). LaTeX is free software and is distributed under the \LaTeX\ Project Public License (LPPL)

\newcommand{\keywords}{\LaTeX}
